---
title: "2018 COGO Summary Report"
subtitle: "Chena River Flood Control Project"
author: "Hannah Vincelette"
date: "8/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE) 
library(ggplot2)
source('Corps_COGO_Sum_Script.R')
```

explanation to be added


### OCCUPANCY

#### Number of boxes unoccupied or occupied by squirrels

* Squirrel occupancy defined by nest boxes with >= 1 squirrel kitten

```{r occupancy1}
o.occupancy
```


#### Number of boxes in which a bird laid >= 1 egg (by species)
```{r occupancy3}
occupancy
```


#### Number of boxes in which a bird incubated >= 1 egg (by species)
* Only considers incubating COGO, BUFF, & COME boxes w/ stage>3 (no dump nests or early abandonment nests)
* Out of the total number of boxes in which a bird laid >= 1 egg

```{r occupancy4}
incub.hen.tab
```

#### Frequency of boxes in which a bird incubated >= 1 egg (by species)
* Only considers incubating COGO, BUFF, & COME boxes w/ stage>3 (no dump nests or early abandonment nests)
* Out of the total number of boxes in which a bird laid >= 1 egg

```{r occupancy4a}
incub.hen.freq
```
#### Occupancy combinations 
* Based boxes in which a bird laid >= 1 egg
* Omits boxes with >2 species
* Will not account for AMKE & OTHER species

```{r occupancy5}
combos
```

### EGGS

#### Total number eggs laid (by species)
```{r eggs1}
total.eggs
```

#### Species clutch stats (by species)
* Species clutch: number of eggs laid in a nest box of the same species as the primary, incubating hen
* Does not consider dump nests
```{r eggs2}
clutch
```


#### Total clutch size stats (by species)
* Total clutch: total number of eggs laid in a nest box (including all species)
* Does not consider dump nests
```{r eggs3}
clutch.tot
```

#### Number of boxes with >1 species of egg (all species)
* Does not take into account if sp1 hen switches throughout the season
```{r eggs4}
boxes.o.eggs
```

#### Number of eggs predated (all species)
* Eggs are assumed predated when they go missing (documented with an "NA"" in the hatched column)
* Does not count ducklings found dead (documented with hatched=1 abd marked=0)
* Does not consider owls

```{r eggs5}
predation.eggs
```

#### Number of boxes predated (all species)
* When >= 1 egg went missing
* Eggs are assumed predated when they go missing (documented with an "NA"" in the hatched column)
* Does not count ducklings found dead (documented with hatched=1 abd marked=0)
* Does not consider owls

```{r eggs6}
predation.boxes
```

### NESTING

#### Nest initiation stats of COGO & BUFF
* Only considers marked boxes
```{r nesting1}
init
```


#### Nest incubation stats of COGO & BUFF
* Only considers marked boxes
```{r nesting3}
incub
```


#### Hatch date stats (by species)
* Only considers marked boxes
* Does not consider BOOW
```{r nesting5}
hatch
```

### NEST SUCCESS

#### Outcomes (by species)
```{r nest.success1}
outcome.sp
```

#### Outcome frequencies (by species)
* Out of the total number of boxes in which a bird laid >= 1 egg 
```{r nest.success2}
outcome.freq
```

#### Number of hatched boxes (by species)
```{r nest.success3}
hatched
```

#### Frequency of hatched boxes (by species)
* Out of the total number of boxes in which a bird laid >= 1 egg 
```{r nest.success4}
freq.hatched
```

#### Plot of hatched boxes over time (totals all species)
* Only considers marked COGO, BUFF, & COME boxes
```{r nest.success5}
print(plot(hatch.days))
```

#### Plot of COGO hatches vs species clutch size
* Species clutch: number of eggs laid in a nest box of the same species as the primary, incubating hen
```{r nest.success6}
print(plot(sp.clutch.tab, ylab="number hatches", xlab ="sp clutch size"))
```

#### Plot of COGO hatches vs total clutch size
* Total clutch: total number of eggs laid in a nest box (including all species)
```{r nest.success7}
print(plot(total.clutch.tab, ylab= "number hatches", xlab ="total clutch size"))
```

#### Plot of COGO hatches vs initatiation date
* Only considers marked boxes
```{r nest.success8}
print(plot(init.hatch.COGO, xlab="initiation date", ylab="number hatched boxes"))
```

### EGG SUCCESS
#### Number of COGO eggs hatched in COGO, BUFF, & COME boxes
```{r egg.success1}
COGO.eggs
```

#### Frequency of COGO eggs hatched in COGO boxes
* Out of total number of COGO eggs hatched
```{r egg.success2}
COGO.eggs.prop
```

#### Number of hatched eggs (by species)
```{r egg.success3}
hatched.sp
```

#### Frequency of hatched eggs (by species)
* Out of total eggs laid by each species
```{r egg.success4}
hatched.freq
```

### HATCHLINGS

#### Number of hatchlings marked (by species)
```{r hatchling1}
marked.sp
```

#### Frequency of hatchlings marked (by species)
* Out of total eggs hatched by each species
```{r hatchling2}
hatched.sp.freq
```

### HEN CAPTURE
#### Hen status (by species)
* Out of total eggs hatched by each species
```{r hen1}
hen.status
```

#### Number of hens with other markers (by species)
* Out of total eggs hatched by each species
```{r hen2}
hen.mark
```


